### 2014-11-13 stat374/hw3.tex
done with hw3

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
STAT 374 HW3 \hfill Aaron Maurer
\vspace{2mm}
\hrule
\vspace{2mm}
\begin{itemize}
    \item[1.]
        \begin{itemize}
            \item[a)]
                \begin{align*}
                    \E[\hat p_{n,s}(x)] &= \E\left[\frac{1}{nh^{s+1}}\sum_{i=1}^n K\left(\frac{X_i-x}{h}\right)\right] \\
                                        &= \frac{1}{h^{s+1}}\int K\left(\frac{u-x}{h}\right)p(u) du\\
                                        &= \frac{1}{h^{s}}\int K\left(u\right)p(x+hu) du\\
                                        &= \frac{1}{h^{s}}\int K(u)\left(\sumj \frac{(hu)^j}{j!}p^{(j)}(x)\right) du\\
                                        &= \sum_{j=1}^{l-1}\frac{h^{j-s}}{j!}p^{(j)}(x)\int K(u)u^j du + \frac{1}{h^{s}}\int K(u)\left(\sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x)\right) du\\
                                        &= p^{(s)}(x)+ \frac{1}{h^{s}}\int K(u)\left(\sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x)\right) du
                \end{align*}
                Using the Lagrange form of the remainder of a Taylor series, for some $\xi\in(x,x+hu)$,
                \[\sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x) = \frac{(hu)^l}{l!}p^{(l)}(\xi)\]
                By the conditions of the H{\"o}lder class,
                \begin{align*}
                    \sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x) &\leq \frac{(hu)^l}{l!}(L\vert \xi - x\vert^{\beta-l} + \vert p(x)\vert) \\
                    \sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x) &\leq \frac{(hu)^l}{l!}(L\vert hu\vert^{\beta-l}  + \vert p(x)\vert) \\
                    \sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x) &\leq h^\beta\frac{u^l\vert u \vert^{\beta-l}L}{l!}+ u^l\frac{h^l}{l!}\vert p(x)\vert \\
                    \sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x) &\leq h^\beta f_1(u)+ u^lf_2(x) \\
                \end{align*}
                For \(f_1(u):=\frac{u^l\vert u \vert^{\beta-l}L}{l!}\) and \(f_2(x):=\frac{h^l}{l!}\vert p(x)\vert\). By similar logic, we also get
                \begin{align*}
                    \sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x) &\geq -\frac{(hu)^l}{l!}(L\vert \xi - x\vert^{\beta-l} + \vert p(x)\vert) \\
                    \sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x) &\geq -h^\beta f_1(u)- u^lf_2(x) 
                \end{align*}

                Plugging these into our expression for \(\E[\hat p_{n,s}(x)]\), we get that 
                \begin{align*}
                    \E[\hat p_{n,s}(x)] &= p^{(s)}(x)+ \frac{1}{h^{s}}\int K(u)\left(\sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x)\right) du \\
                    \vert \E[\hat p_{n,s}(x)]-p^{(s)}(x) \vert &\leq \frac{1}{h^{s}}\int K(u) (h^\beta f_1(u)+ u^lf_2(x)) du \\
                                                                &\leq h^{\beta-s}\int K(u) f_1(u) du + \frac{f_2(x)}{h^{s}}\int K(u) u^l du\\
                                                                &\leq h^{\beta-s}c
                \end{align*}

                For \(c:=\int K(u) f_1(u) du\), showing the bias is bounded as desired.
            \item[b)]
                Combining the bounds on bias squared and variance from part a) to get the risk, we get
                \begin{align*}
                    \mbox{max}(\L^2(\hat P_{n,s}(x))) &= c^2h^{2(\beta-s)}+\frac{c'}{nh^{2s+1}} \\
                    \frac{d}{dh}\mbox{max}((\L^2(\hat P_{n,s}(x))) &= 2(\beta-s)c^2h^{2(\beta-s)-1}-\frac{(2s+1)c'}{nh^{2s+2}} 
                \end{align*}
                Then, this risk bound is minimized when its derivative is at $0$, so for the optimal $h$,
                \begin{align*}
                    0 &= 2(\beta-s)c^2h^{2(\beta-s)-1}-\frac{(2s+1)c'}{nh^{2s+2}} \\
                    \frac{(2s+1)c'}{2(\beta-s)c^2}\frac{1}{n} &= h^{2\beta+1} \\
                    \left(\frac{(2s+1)c'}{2(\beta-s)c^2}\right)^\frac{1}{2\beta+1}n^{-\frac{1}{2\beta+1}} &= h 
                \end{align*}
                Plugging this into the original risk function, and defining a new constant \(c_1=\left(\frac{(2s+1)c'}{2(\beta-s)c^2}\right)^\frac{1}{2\beta+1}\), we get
                \begin{align*}
                    \mbox{max}(\L^2(\hat P_{n,s}(x)))  &= c^2c_1^{2(\beta-s)}n^{\frac{2(\beta-s)}{2\beta+1}}-\frac{c'}{c^{2s+1}}n^{\frac{2s+1-2\beta+1}{2\beta+1}} \\
                    \mbox{max}(\L^2(\hat P_{n,s}(x))) &= \left(c^2c_1^{2(\beta-s)}+\frac{c'}{c^{2s+1}}\right)n^{\frac{2(\beta-s)}{2\beta+1}}
                \end{align*}
                So the maximum risk is of order \(O\left(n^{\frac{2(\beta-s)}{2\beta+1}}\right)\).
        \end{itemize}
    \item[2.]
        \begin{itemize}
            \item[a)]
                \begin{align*}
                    L_F(x)&=\lim_{\epsilon\to 0} \frac{T((1-\epsilon)F+\epsilon\delta_x)-T(F)}{\epsilon} \\
                    L_F(x)&=\lim_{\epsilon\to 0} \frac{((1-\epsilon)F(b)+\epsilon\delta_x(b))-((1-\epsilon)F(a)+\epsilon\delta_x(a))-(F(b)-F(a))}{\epsilon} \\
                    L_F(x)&=\lim_{\epsilon\to 0} \frac{\epsilon(I_{[x,\infty)}(b)-I_{[x,\infty)}(a))-\epsilon (F(b)-F(a))}{\epsilon} \\
                    L_F(x)&= I_{[a,b)}(x)-T(F) \\
                \end{align*}
            \item[b)]
                \begin{align*}
                    \hat{se}(\hat \theta) &= \frac{\hat \tau}{\sqrt{n}} \\
                    \hat{se}(\hat \theta) &= \frac{1}{n^\frac{3}{2}}\sum_{i=1}^n(I_{[a,b)}(X_i)-T(\hat F_n))^2 \\
                    \hat{se}(\hat \theta) &= \frac{1}{n^\frac{3}{2}}\sum_{i=1}^n(I_{[a,b)}(X_i)-\hat F_n(b)+\hat F_n(a))^2 \\
                    \hat{se}(\hat \theta) &= \frac{1}{\sqrt{n}}\left((\hat F_n(b)-\hat F_n(a))(1-\hat F_n(b)+\hat F_n(a))^2+(1-\hat F_n(b)+\hat F_n(a))(\hat F_n(b)-\hat F_n(a))^2\right) \\
                    \hat{se}(\hat \theta) &= \frac{1}{\sqrt{n}}\left((\hat F_n(b)-\hat F_n(a)+1- \hat F_n(b)+\hat F_n(a))(\hat F_n(b)-\hat F_n(a))(1-\hat F_n(b)+\hat F_n(a))\right) \\
                    \hat{se}(\hat \theta) &= \frac{1}{\sqrt{n}}\left((\hat F_n(b)-\hat F_n(a))(1-\hat F_n(b)+\hat F_n(a))\right) \\
                \end{align*}
            \item[c)]
                An approximate \(1-\alpha\) confidence interval is given by 
                \[\hat \theta \pm z_{\frac{\alpha}{2}}\hat{se}(\hat \theta) = F_n(b)-\hat F_n(a) \pm z_{\frac{\alpha}{2}}\frac{1}{\sqrt{n}}\left((\hat F_n(b)-\hat F_n(a))(1-\hat F_n(b)+\hat F_n(a))\right)\]
            \item[d)]
                To estimate \(se(\hat \theta)\), one would draw a sample, with replacement, of $n$ from the $X_i$s. For each of these samples, $\hat\theta$ would be calculated (this is the portion of the sample in \([a,b)\). Then, \(se(\hat \theta)\) is the standard deviation of $\hat\theta$ among all the samples.

>>>>

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
STAT 374 HW3 \hfill Aaron Maurer
\vspace{2mm}
\hrule
\vspace{2mm}
\begin{itemize}
    \item[1.]
        \begin{itemize}
            \item[a)]
                \begin{align*}
                    \E[\hat p_{n,s}(x_0)] &= \E\left[\frac{1}{nh^{s+1}}\sum_{i=1}^n K\left(\frac{X_i-x_0}{h}\right)\right] \\
                                        &= \frac{1}{h^{s+1}}\int K\left(\frac{u-x_0}{h}\right)p(u) du\\
                                        &= \frac{1}{h^{s}}\int K\left(u\right)p(x_0+hu) du\\
                                        &= \frac{1}{h^{s}}\int K(u)\left(\sum_{j=0}^\infty \frac{(hu)^j}{j!}p^{(j)}(x_0)\right) du\\
                                        &= \sum_{j=0}^{l-1}\frac{h^{j-s}}{j!}p^{(j)}(x_0)\int K(u)u^j du + \frac{1}{h^{s}}\int K(u)\left(\sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x_0)\right) du\\
                                        &= p^{(s)}(x_0)+ \frac{1}{h^{s}}\int K(u)\left(\sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x_0)\right) du
                \end{align*}
                Using the Lagrange form of the remainder of a Taylor series, for some $\xi\in(x_0,x_0+hu)$,
                \[\sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x_0) = \frac{(hu)^l}{l!}p^{(l)}(\xi)\]
                By the conditions of the H{\"o}lder class,
                \begin{align*}
                    \sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x_0) &\leq \frac{(hu)^l}{l!}(L\vert \xi - x_0\vert^{\beta-l} + \vert p(x_0)\vert) \\
                    \sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x_0) &\leq \frac{(hu)^l}{l!}(L\vert hu\vert^{\beta-l}  + \vert p(x_0)\vert) \\
                    \sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x_0) &\leq h^\beta\frac{u^l\vert u \vert^{\beta-l}L}{l!}+ u^l\frac{h^l}{l!}\vert p(x_0)\vert \\
                    \sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x_0) &\leq h^\beta f_1(u)+ u^lf_2(x_0) \\
                \end{align*}
                For \(f_1(u):=\frac{u^l\vert u \vert^{\beta-l}L}{l!}\) and \(f_2(x_0):=\frac{h^l}{l!}\vert p(x_0)\vert\). By similar logic, we also get
                \begin{align*}
                    \sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x_0) &\geq -\frac{(hu)^l}{l!}(L\vert \xi - x_0\vert^{\beta-l} + \vert p(x_0)\vert) \\
                    \sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x_0) &\geq -h^\beta f_1(u)- u^lf_2(x_0) 
                \end{align*}

                Plugging these into our expression for \(\E[\hat p_{n,s}(x_0)]\), we get that 
                \begin{align*}
                    \E[\hat p_{n,s}(x_0)] &= p^{(s)}(x_0)+ \frac{1}{h^{s}}\int K(u)\left(\sum_{j=l}^\infty \frac{(hu)^j}{j!}p^{(j)}(x_0)\right) du \\
                    \vert \E[\hat p_{n,s}(x_0)]-p^{(s)}(x_0) \vert &\leq \frac{1}{h^{s}}\int K(u) (h^\beta f_1(u)+ u^lf_2(x_0)) du \\
                                                                &\leq h^{\beta-s}\int K(u) f_1(u) du + \frac{f_2(x_0)}{h^{s}}\int K(u) u^l du\\
                                                                &\leq h^{\beta-s}c
                \end{align*}

                For \(c:=\int K(u) f_1(u) du\), showing the bias is bounded as desired. To bound the variance term, we have that
                \begin{align*}
                    \var\left(\hat p_{n,s}(x_0)\right) &= \frac{1}{nh^{2s+2}}\var\left(K\left(\frac{X_i-x_0}{h}\right)\right) \\
                                                     &= \frac{1}{nh^{2s+2}}\left(\E\left[K\left(\frac{X_i-x_0}{h}\right)^2\right]-\E\left[K\left(\frac{X_i-x_0}{h}\right)\right]^2\right) \\
                                                     &\leq \frac{1}{nh^{2s+2}}\left(h\int K^2(u)\left(\sum_{j=0}^\infty \frac{(hu)^j}{j!}p^{(j)}(x_0)\right)du-\left(h^{s+1}p^{(s)}(x_0)+ h^{\beta+1}c\right)^2\right) \\
                                                     &\leq \frac{p(x_0)}{nh^{2s+1}}\int K^2(u)du + O\left(\frac{1}{n}\right)
                \end{align*}
                So \(\var\left(\hat p_{n,s}(x_0)\right)\) is bounded by \(\frac{c'}{nh^{2s+1}}\) for \(c'>0\).
            \item[b)]
                Combining the bounds on bias squared and variance from part a) to get the risk, we get
                \begin{align*}
                    \mbox{max}(\L^2(\hat P_{n,s}(x))) &= c^2h^{2(\beta-s)}+\frac{c'}{nh^{2s+1}} \\
                    \frac{d}{dh}\mbox{max}((\L^2(\hat P_{n,s}(x))) &= 2(\beta-s)c^2h^{2(\beta-s)-1}-\frac{(2s+1)c'}{nh^{2s+2}} 
                \end{align*}
                Then, this risk bound is minimized when its derivative is at $0$, so for the optimal $h$,
                \begin{align*}
                    0 &= 2(\beta-s)c^2h^{2(\beta-s)-1}-\frac{(2s+1)c'}{nh^{2s+2}} \\
                    \frac{(2s+1)c'}{2(\beta-s)c^2}\frac{1}{n} &= h^{2\beta+1} \\
                    \left(\frac{(2s+1)c'}{2(\beta-s)c^2}\right)^\frac{1}{2\beta+1}n^{-\frac{1}{2\beta+1}} &= h 
                \end{align*}
                Plugging this into the original risk function, and defining a new constant \(c_1=\left(\frac{(2s+1)c'}{2(\beta-s)c^2}\right)^\frac{1}{2\beta+1}\), we get
                \begin{align*}
                    \mbox{max}(\L^2(\hat P_{n,s}(x)))  &= c^2c_1^{2(\beta-s)}n^{\frac{2(\beta-s)}{2\beta+1}}-\frac{c'}{c^{2s+1}}n^{\frac{2s+1-2\beta+1}{2\beta+1}} \\
                    \mbox{max}(\L^2(\hat P_{n,s}(x))) &= \left(c^2c_1^{2(\beta-s)}+\frac{c'}{c^{2s+1}}\right)n^{\frac{2(\beta-s)}{2\beta+1}}
                \end{align*}
                So the maximum risk is of order \(O\left(n^{\frac{2(\beta-s)}{2\beta+1}}\right)\).
        \end{itemize}
    \item[2.]
        \begin{itemize}
            \item[a)]
                \begin{align*}
                    L_F(x)&=\lim_{\epsilon\to 0} \frac{T((1-\epsilon)F+\epsilon\delta_x)-T(F)}{\epsilon} \\
                    L_F(x)&=\lim_{\epsilon\to 0} \frac{((1-\epsilon)F(b)+\epsilon\delta_x(b))-((1-\epsilon)F(a)+\epsilon\delta_x(a))-(F(b)-F(a))}{\epsilon} \\
                    L_F(x)&=\lim_{\epsilon\to 0} \frac{\epsilon(I_{[x,\infty)}(b)-I_{[x,\infty)}(a))-\epsilon (F(b)-F(a))}{\epsilon} \\
                    L_F(x)&= I_{[a,b)}(x)-T(F) \\
                \end{align*}
            \item[b)]
                \begin{align*}
                    \hat{se}(\hat \theta) &= \frac{\hat \tau}{\sqrt{n}} \\
                    \hat{se}(\hat \theta) &= \frac{1}{n^\frac{3}{2}}\sum_{i=1}^n(I_{[a,b)}(X_i)-T(\hat F_n))^2 \\
                    \hat{se}(\hat \theta) &= \frac{1}{n^\frac{3}{2}}\sum_{i=1}^n(I_{[a,b)}(X_i)-\hat F_n(b)+\hat F_n(a))^2 \\
                    \hat{se}(\hat \theta) &= \frac{1}{\sqrt{n}}\left((\hat F_n(b)-\hat F_n(a))(1-\hat F_n(b)+\hat F_n(a))^2+(1-\hat F_n(b)+\hat F_n(a))(\hat F_n(b)-\hat F_n(a))^2\right) \\
                    \hat{se}(\hat \theta) &= \frac{1}{\sqrt{n}}\left((\hat F_n(b)-\hat F_n(a)+1- \hat F_n(b)+\hat F_n(a))(\hat F_n(b)-\hat F_n(a))(1-\hat F_n(b)+\hat F_n(a))\right) \\
                    \hat{se}(\hat \theta) &= \frac{1}{\sqrt{n}}\left((\hat F_n(b)-\hat F_n(a))(1-\hat F_n(b)+\hat F_n(a))\right) \\
                \end{align*}
            \item[c)]
                An approximate \(1-\alpha\) confidence interval is given by 
                \[\hat \theta \pm z_{\frac{\alpha}{2}}\hat{se}(\hat \theta) = F_n(b)-\hat F_n(a) \pm z_{\frac{\alpha}{2}}\frac{1}{\sqrt{n}}\left((\hat F_n(b)-\hat F_n(a))(1-\hat F_n(b)+\hat F_n(a))\right)\]
            \item[d)]
                To estimate \(se(\hat \theta)\), one would draw a sample, with replacement, of $n$ from the $X_i$s. For each of these samples, $\hat\theta$ would be calculated (this is the portion of the sample in \([a,b)\). Then, \(se(\hat \theta)\) is the standard deviation of $\hat\theta$ among all the samples.
